---
title: "_'How the Public Defines Terrorism'_ <br/> by Connor Huff and Joshua Kertzer"
author: _Keeley MacAfee_
date: "4/29/2019"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
---

```{r setup, include=FALSE}
library(xaringanthemer)
library(knitr)
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include = FALSE}
mono_light(
  base_color = "#23395b",
  header_font_google = google_font("Arial"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Droid Mono")
)
```

class: center
# What is terrorism?
.left[
- According to the New Oxford American Dictionary, terrorism is "the unlawful use of violence and intimidation, especially against civilians, in the pursuit of political aims."

- In reality, the definition is up for debate. Academics, policy makers, and members of the public disagree about what counts as terrorism. 
]
---

class: center
# Why does the definition of terrorism matter?

.left[
- "If the responses of ordinary citizens constitute a central causal mechanism through which terrorrism operates, it logically follows that understanding what ordinary citizens think terrorism is is a crucial prerequisite to understanding how they react to it" (Huff and Kertzer 55). 
  
  - Media coverage impacts public opinion. Public opinion impacts policy.  

- Lack of agreement on definition leaves ambiguity in decisions regarding prosecution, sanctions, and treaties for combating terrorism.
  
  - Terrorism is understood as an exceptional act mandating an exceptional response. 

- The definition of terrorism and the image of the terrorist impact people's behavior towards one another as well as their preferences on laws, elections, and policies.
  ]
---

class: center 

# A Typology for Classifying Terrorism
.left[
Huff and Kertzer use two sets of criteria:
1. Objective criteria
  - Severity of violence, target, location
  
2. Subjective criteria
  - Motivation, who the perpetrator is
  
- Time between the occurrence of the incident and the release of details surrounding it cause issues of availability and public perception. 

- Seeking to directly assess how ordinary people define terrorism by examining the perception of different attributes of an incident.
]
---
class: center
# Methods

.left[

- Present participants with a series of incidents with randomly generated features then ask if they think it is terrorism or not. 

- Manipulate seven attributes of an incident: tactics, casualties, target, location, actor, categorization of actor, and motivation. 

  - _Example_: The incident: a shooting. The shooting occurred at a church in a foreign democracy with a history of human rights violations. There were two individuals killed in the shooting. The shooting was carried out by a Muslim individual with a history of mental illness. News reports suggest the individual had been in an ongoing personal dispute with one of the targets.
  
- Used Amazon's Mechanical Turk (MTurk) to field the survey in August 2015 and reached 1,400 respondents. _Note:_ Since 1,400 participants respond to seven incidents each, the analyses are based on 9,800 randomly generated scenarios. 
]

---
class: center
# The Effect of Tactics
.left[
- Type of tactic used plays a central role in whether an incident is perceived as terrorism or not.]

```{r echo=FALSE, warning=FALSE}
include_graphics("fig2a.pdf")
```

---
class: center
# The Effect of Casualties
.left[
- The number of casualties, or severity of the violence, is less central.]

```{r echo=FALSE, warning=FALSE, fig.pos="p"}
include_graphics("fig2b.pdf")
```

---
class: center
# Location of Incident
.left[
- Location does not generally have an effect on whether an incident is classified as terrorism or not.] 

```{r echo=FALSE, warning=FALSE}
include_graphics("fig3a.pdf")
```
---
class: center
# Target of Incident
.left[
- Nore does the target of the incident.]

```{r echo=FALSE, warning=FALSE}
include_graphics("fig3b.pdf")
```

---
class: center
# The Political Purposiveness of the Perpetrator
.left[
- Two main themes: acts carried out by collectives are more likely to be considered terrorism than those carried out by individuals and acts carried out by individuals with a history of mentall illness are less likely to be seen as terrorism.]

```{r echo=FALSE, warning=FALSE}
include_graphics("fig4.pdf")
```

---
class: center
# Social Categorization Effects
.left[
- Details regarding social categorization of the perpetrator of an incident impact how the incident is perceived.
]

```{r echo=FALSE, warning=FALSE}
include_graphics("fig5.pdf")
```

---
class: center
# Motive Attribution Effects
.left[
- Incidents driven, in some way, by political motivations are increasingly more likely to be classified as terrorism.
]
```{r echo=FALSE, warning=FALSE}
include_graphics("fig6.pdf")
```

---
# Applications

- Mapping onto Real-World Events

- Demonstrating Framing Effects

- Analyzing Media Coverage 

---

# Conclusion

- Terrorism vs. "small" forms of violence

- Objective and subjective criteria have fairly equal impacts on the public's understanding of acts of terrorism.

- The media has a significant role in influencing how the public classifies violent events. 

- Terrorism is not exclusive to targeting civilians, nor does it always entail political motivations. 

---

# Possible Extensions
- Examine competing media frames

- Additional analysis of media coverage, specifically pertaining to ratings and coverage of perpetrators 

- Explore political frames

- Comparison with foreign public perceptions
